---
title: "Replications of Table 5 (AK)"
output:
  pdf_document: 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error=TRUE)
library(here)
library(xglue)
```

# Main Replications

We replicate Table 5 for different data sets. As in BCH, all observations with $z>10$ were dropped for these replications. This RMD file only prints the resulting tables. To perform the computation, source the file `ak_table.R` and then run the function `make.ak.tables()`.

Note that in Panel B the actual 3rd interval used by BCH was from [1.96,2.33], even though [1.96, 2.58] was stated. We replicate based on the actual interval used: [1.96, 2.33].

## Orginal data supplement in BCH AER article

```{r results="asis"}
res = readLines(here("Results", "tab_bch_ak_aer_10.tex"))
cat(res)
```

The table above should be identical to Table 5 in the AER article.

## Updated data without rounding adjustment

```{r results="asis"}
res = readLines(here("Results", "tab_bch_ak_new_10.tex"))
cat(res)
```


## Updated data with rounding adjustment
We drop all observations with $s < 37$.

```{r results="asis"}
res = readLines(here("Results", "tab_bch_ak_drop_10.tex"))
cat(res)
```

# Alternative replications dropping only z > 100

In the published do file by BCH they only drop z > 100 (but that was not the code run to generate the tables in the AER article). We replicate now the 3 tables above for this selection.

Results are still qualitatively similar. By comparing the tables, we see however that the decision to drop z > 100 or z > 10 has a bigger impact on the estimates than our rounding adjustment.

## Orginal data supplement in BCH AER article

```{r results="asis"}
res = readLines(here("Results", "tab_bch_ak_aer_100.tex"))
cat(res)
```

## Updated data without rounding adjustment

```{r results="asis"}
res = readLines(here("Results", "tab_bch_ak_new_100.tex"))
cat(res)
```


## Updated data with rounding adjustment 

We drop all observations with $s < 37$.

```{r results="asis"}
res = readLines(here("Results", "tab_bch_ak_drop_100.tex"))
cat(res)
```


# AK Specification tests: Correlations

```{r results = "asis"}
library(xglue)

df = read.csv(here("Data", "ak_cor_sum.csv"))
fo = function(x) format(round(x,2), nsmall=2)
dat = df %>% 
  mutate(
    ci.low = fo(ci.low),
    ci.up = fo(ci.up),
    cor = fo(cor),
    ci = paste0("[", ci.low, ", ", ci.up,"]")
  )

methods = c("DID","IV","RCT","RDD")
d = function(panel, dataset, col) {
  rows = dat$panel == panel & dat$dataset==dataset
  dat[[col]][rows]
}

tpl = readLines(here("Tex_templates","tab_ak_cor_tpl.tex"))
res = xglue(tpl, open="<<", close=">>")
writeLines(res, here("Results", "tab_ak_cor.tex"))
res

```

