---
title: "Comment and Working Paper Figures and Tables not created elsewhere"
output: 
  pdf_document: 
    df_print: kable    
    keep_tex: yes
---

```{r setup, include=FALSE}
#setwd("C:/research/comment_phack/")
library(dplyr)
library(ggplot2)
library(RoundingMatters)
library(dplyrExtras)
library(here)
knitr::opts_chunk$set(echo = FALSE, error=TRUE, warn=FALSE, cache=FALSE, fig.width=5.5, fig.height=3.2,fig.path = here("Results/",""))
options(dplyr.summarise.inform = FALSE)

ggtitle = function(label,...) {ggplot2::ggtitle("")}

dat = readRDS(here("Data","MM_new.Rds"))

wdat = readRDS(here("Data","deround_binom_ci.Rds"))
#wdat = readRDS(here("Data","deround_t_ci.Rds"))
unique(wdat$mode)
wdat= wdat %>% mutate_rows(mode=="reported", mode="org") %>%
  mutate(share_signif = theta)

h.bch = c(0.05,0.075,0.1,0.2,0.3,0.4,0.5)
```

# 0 Basic statistics

### Share of reported mu / sigma, t, p and CI
```{r }
dat %>% 
  group_by(report) %>%
  summarize(
    n = n(),
    share = n / sum(!is.na(dat$report))
  )
```


# 1 The rounding problem and our solution in the pooled data

### Figure 1 Combined in Two panels

```{r "share_of_significant_tests", fig.height=2.5, fig.width=5.5}
df = filter(wdat, method=="ALL", mode %in% c("org","omit")) %>%
  mutate(type = ifelse(mode=="org","BCH","Our Adjustment")) %>%
  mutate(type = relevel(as.factor(type),"BCH"))

ggplot(df, aes(x=h, y= share_signif)) +
  geom_vline(xintercept = h.bch, col="grey") +
  geom_hline(yintercept = 0.5, col="blue") +
  coord_cartesian(ylim=c(0.3, 0.7)) +
  geom_ribbon(data = filter(df,h<=0.04), mapping=aes(ymin = ci.low, ymax = ci.up), alpha=0.3) +
  geom_ribbon(data = filter(df,h>0.04), mapping=aes(ymin = ci.low, ymax = ci.up), alpha=0.3) +
  geom_point() + theme_bw() + ylab("Share of tests with z >= 1.96") +
  xlab("Window half-width h")+ggtitle("All Methods") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  facet_wrap(~type)
```


### Figure 2: Number of included observations

```{r "number_of_included_observations", fig.height=3,  fig.width=5.5}
df = filter(wdat, method=="ALL", mode %in% c("org","omit")) %>%
  mutate(mode = ifelse(mode=="org","BCH","Our Adjustment")) %>%
  mutate(mode = relevel(as.factor(mode),"BCH"))

ggplot(df, aes(x=h, y= obs)) + geom_vline(xintercept = h.bch, col="grey") + geom_point() + theme_bw() + ylab("") + xlab("Window half-width h")+ggtitle("Number of included observations (all methods)") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + facet_wrap(~mode)
```

### Share of obs with z==2 in smallest window

```{r echo=TRUE}
sum(dat$z==2, na.rm=TRUE)
d = filter(dat, abs(z-1.96)<=0.05)
sum(d$z==2, na.rm=TRUE)
sum(d$z==2, na.rm=TRUE) / NROW(d)


```


## Table of significant digits of standard error

```{r include=FALSE}
dat$nsig.sd = nchar(as.character(abs(dat$s)))
dat %>%  group_by(nsig.sd) %>% summarize(count=n()) %>% arrange(nsig.sd)
dat %>% 
  mutate(nsig = ifelse(nsig.sd %in% 0:6, nsig.sd,100)) %>%
  group_by(nsig) %>% summarize(count=n()) %>% arrange(nsig)

dat %>%  group_by(nsig.sd) %>% summarize(count=n()) %>% arrange(nsig.sd)
```

### Share digits

```{r "share_sig_digits"}
as.perc = function(x, digits=1) paste0(round(x*100,digits),"%")
dat = dat %>% mutate(
    subset = ifelse(z==2,"z is 2","z is not 2")
  )
tab = dat %>%
  group_by(subset) %>%
  summarize(
    obs=n(),
    single_signif_sd = as.perc(mean(nsig.sd==1, na.rm=TRUE)),
    single_or_double_signif_sd = as.perc(mean(nsig.sd<=2, na.rm=TRUE))
  )
tab
```


### Correlation s <= 37 and z

```{r echo=TRUE}
cor.test(dat$z, 1L*(!dat$keep.obs))

dat.omit = dat %>% select(mu,z, sigma) %>% filter(is.finite(z), is.finite(sigma))
cor.test(dat.omit$z, dat.omit$sigma)

dat.omit = filter(dat.omit,z >0, sigma > 0)
cor.test(log(dat.omit$z), dat.omit$sigma)

```

### Table of omitted obs

```{r}
dat$omit = !dat$keep.obs

res = dat %>%
  group_by(z) %>%
  mutate(count.z = n()) %>%
  mutate(group = case_when(
    z == 2 ~ "z=2",
    count.z >= 10 ~ "other bunching",
    TRUE ~ "no bunching"
  )) %>%
  group_by(group) %>%
  summarize(
    count = n(),
    share.omit = paste0(round(100*sum(omit, na.rm=TRUE) / n(),1),"%")
  ) %>%
  arrange(count) %>%
  select(group, count, share.omit)
res


dat %>%
  ungroup() %>%
  summarize(
    count = n(),
    share.omit = paste0(round(100*sum(omit, na.rm=TRUE) / n(),1),"%")
  )

```

```{r "observations_at_risk", fig.height=2.5, fig.width=6}
library(stringtools)
library(forcats)
library(ggplot2)
risks = rounding.risks(z = dat$z, s=dat$s, z0=1.96, h=0.1)

dr = rounding.risks.summary(risks) %>% 
  filter(error.type != "any") %>%
  mutate(Side = ifelse(side=="below","z < 1.96","z >= 1.96"))

colors = rev(c("#aaaaaa","#000000"))

ggplot(dr, aes(x=s.bar,y=risk, color=Side)) +
  geom_vline(xintercept = 37, col="#888888") +
  geom_line(size=1.2, alpha=0.7) +
  theme_bw() +
  ylab("Share of observations at risk") +
  xlab("Ommission threshold for s") +
  ggtitle("Risk of wrongful inclusion") +
  facet_wrap(~error.lab) +
  scale_y_continuous(breaks = seq(0,0.5,by=0.1))+
  scale_color_manual(values=colors) 
  

```



### Table of most common bunched z-values

```{r include = FALSE}
library(dplyr)
res = dat %>%
  group_by(z) %>%
  summarise(count = n(), dist=first(abs(z-1.96))) %>%
  ungroup() %>%
  arrange(-count) %>%
  filter(count >= 10)
res
```


# Counts by method

```{r}
dat %>%
  mutate(in.window = abs(z-1.96) <= 0.05) %>%
  group_by(method) %>%
  summarize(
    total.obs = n(),
    obs.with.z2 = sum(z==2),
    share.z2.in.window = round(100*obs.with.z2 / sum(in.window),1)
  )
```


# RCT shares of significant tests in window for caliper tests

Used for last line in Caliper table.
```{r echo=TRUE}
rct = filter(dat, method=="RCT",keep.obs)
rct %>% filter(abs(z-1.96)<=0.5) %>% summarize( mean(z >= 1.96))
rct %>% filter(abs(z-1.96)<=0.35) %>% summarize( mean(z >= 1.96))
rct %>% filter(abs(z-1.96)<=0.2) %>% summarize( mean(z >= 1.96))


```


# Power analyis: size of confidence intervals

```{r results="asis"}
df = readRDS(here("Data","deround_binom_ci.Rds"))

temp = filter(df, method=="DID")
h.bch = c(0.05,0.075,0.1,0.2,0.3,0.4,0.5)

ci.df = df %>% 
  filter(round(h*1000) %in% round(h.bch*1000)) %>%
  mutate(ci.width = ci.up -ci.low) %>% 
  group_by(h, method) %>%
  mutate(ci.inc = ci.width / ci.width[mode=="reported"] -1) %>%
  filter(mode %in% c("omit", "reported")) %>%
  group_by(method, mode) %>%
  summarize(
    obs = mean(obs),
    w = mean(ci.width),
    inc = mean(ci.inc)
  )
org.df = filter(ci.df, mode == "reported") %>% select(-inc)
names(org.df)[3:4] = c("org_obs","org_w")
om.df = filter(ci.df, mode == "omit")
names(om.df)[3:4] = c("om_obs","om_w")

dat = org.df %>% left_join(om.df,b="method")
dat$m = dat$method
dat$method[1] = "Pooled"
dat$inc = paste0(round(100*(dat$inc),1),"\\%")

library(xglue)
tpl = readLines(here("Tex_templates","tab_power_tpl.tex"))
res = xglue(tpl, open="<<", close=">>")
writeLines(res, here("Results", "power_tab.tex"))
cat(res)
```

# Increases for DID sample for all h
```{r}
df %>% 
  filter(round(h*1000) %in% round(h.bch*1000)) %>%
  mutate(ci.width = ci.up -ci.low) %>% 
  group_by(h, method) %>%
  mutate(ci.inc = ci.width / ci.width[mode=="reported"] -1) %>%
  filter(mode %in% c("omit","reported"), method=="DID") %>%
  select(h, ci.width, ci.inc,obs)
```

